Capturing Subdiffusive Solute Dynamics and Predicting Selectivity in Nanoscale Pores with Time Series Modeling

### 2020-04-28 Ben_Manuscripts/stochastic_transport/cover_letter_JCTC.tex
update cover letter.

	We are submitting ``\ManuscriptTitle'' by Benjamin J. Coscia
        and Michael R.  Shirts, for consideration for publication as
        an Article in the Journal of Chemical Theory and
        Computation. We expect this work to be of significant interest
        to researchers who study complex transport at the molecular
        level by adding important new techniques for estimating long
        time scale behavior, inferring mechanisms, and estimating bulk
        transport behavior from molecular trajectories. Please note that this article has been uploaded to arXiv with
	differences only in formatting: \href{https://arxiv.org/abs/2004.07905}{https://arxiv.org/abs/2004.07905}. \\

	In this article, we analyze solute trajectories generated from
        5$\mu$s molecular dynamics (MD) simulations of an inverted
        hexagonal (H\textsubscript{II}) phase self-assembled lyotropic
        liquid crystal (LLC) polymer membrane to parameterize two
        different stochastic time series approaches capable of
        predicting solute flux and selectivity on a macroscopic
        scale. Both approaches quantitatively reproduce the mean
        squared displacements (MSDs) exhibited by solutes in MD
        simulations. This is among the first studies to apply time
        series modeling of molecular simulations in order to infer
        mechanisms, propagate behavior to long time scaless and,
        estimate bulk materials properties.\\

>>>>

	We are submitting ``\ManuscriptTitle'' by Benjamin J. Coscia
        and Michael R.  Shirts, for consideration for publication as
        an Article in the Journal of Chemical Theory and
        Computation. We expect this work to be of significant interest
        to researchers who study complex transport at the molecular
        level by adding important new techniques for estimating long
        time scale behavior and bulk transport behavior from shorter
        molecular trajectories exhibiting anomalous diffusion rather
        than Brownian motion. Please note that this article has been
        uploaded to arXiv with differences only in formatting:
        \href{https://arxiv.org/abs/2004.07905}{https://arxiv.org/abs/2004.07905}. \\

	In this article, we analyze solute trajectories generated from
        5$\mu$s molecular dynamics (MD) simulations of an inverted
        hexagonal (H\textsubscript{II}) phase self-assembled lyotropic
        liquid crystal (LLC) polymer membrane to parameterize two
        different stochastic time series approaches capable of
        predicting solute flux and selectivity on a macroscopic
        scale. Both approaches quantitatively reproduce the mean
        squared displacements (MSDs) exhibited by solutes in MD
        simulations. This is among the first studies to apply time
        series modeling of molecular simulations in order to infer
        propagate behavior to long time scales and estimate bulk
        materials properties with complex anomalous diffusion
        mechanisms.\\
